\input{Tables/Table_IGDP_2obj.tex}
\input{Tables/Tests_IGDP_2obj.tex}
\input{Tables/Tests_IGDP_3obj.tex}

This section presents the results obtained by \VSDMOEA{} and state-of-the-art schemes in terms of
the IGD+\cite{Joel:Inverted_Generational_Distance_Plus}.
%
Specifically, we present the results for the long-term executions, meaning
the stopping criterion was set to $250,000$ generations.
%
The structure of the tables is the same as in the main document.
%
Thus, the only modification is that instead of using the hypervolume, the IGD+ is used.

Table \ref{tab:StatisticsIGDP_2obj} shows the IGD+ obtained for the benchmark functions with two objectives.
%
Specifically, the minimum, maximum, mean and standard deviation of the IGD+ is given for each method and function tested.
%
The last row shows the results considering all the functions together.
%
For each function, the data for the method that yielded the lowest mean is shown in bold.
%
Additionally, all the methods that were not statistically inferior to said method are shown in bold.
%
From here on, the methods shown in bold for a given problem are referred to as the winning methods.
%
Based on the number of functions where each method is in the group of the winning methods for the cases 
with two objectives, the best methods are \VSDMOEA{} and \RMOEA{} with 13 and 8, respectively.
%
Thus, \VSDMOEA{} is the most competitive method in terms of this metric.
%
More impressive is the fact that the mean IGD+ attained by \VSDMOEA{}, when all the problems are considered simultaneously, is much lower 
than that attained by \RMOEA{}.
%
In fact, the total means of \RMOEA{} ($0.060$), \NSGAII{} ($0.051$) and \MOEAD{} ($0.062$) are quite similar.
%
In contrast, \VSDMOEA{} yielded a much lower value ($0.021$).
%
When the data is inspected carefully, it is clear that in the cases where \VSDMOEA{} loses, the difference with respect to the
best method is not very large.
%
For instance, the difference between the mean IGD+ attained by \VSDMOEA{} and by the best method was never larger
than $0.05$.
%
However, all the other methods exhibited a deterioration greater than $0.05$ in several cases.
%
Specifically, it happened in $7$, $5$ and $8$ problems for \MOEAD{}, \NSGAII{} and \RMOEA{}, respectively.
%
This means that even if \VSDMOEA{} loses in some cases, its deterioration is always small, exhibiting a much more 
robust behavior than any other method.
%
Exactly the same situation appeared when analyzing the data in terms of hypervolume.

In order to better clarify these findings, pair-wise statistical tests were done between each method tested in each 
function.
%
Table~\ref{tab:Tests_IGDP_2obj} shows the results, with the same meaning as in the main document.
%
The calculated data confirms that although \VSDMOEA{} loses in some cases, the overall numbers of wins and losses favor \VSDMOEA{}.
%
More importantly, the total deterioration is considerably lower in the case of \VSDMOEA{}, confirming that when \VSDMOEA{} loses, the deterioration is not 
very high.


Tables~\ref{tab:Tests_IGDP_3obj} and~\ref{tab:StatisticsIGDP_3obj} show the same information for the problems with three objectives.
%
In this case, the superiority of \VSDMOEA{} is even clearer.
%
Taking into account the mean of all the functions, \VSDMOEA{} again yielded a much lower mean IGD+ than the other methods.
%
Specifically, \VSDMOEA{} obtained a value of $0.059$, whereas the second-ranked algorithm (\RMOEA{}) obtained a value of $0.093$.
%
Once again, the difference between the mean IGD+ obtained by \VSDMOEA{} and by the best method was never greater
than $0.05$.
%
However, all the other methods exhibited a deterioration greater than $0.05$ in several cases.
%
In particular, this happened in $5$, $8$ and $7$ problems for \MOEAD{}, \NSGAII{}, \RMOEA{}, respectively.
%
Moreover, \VSDMOEA{} is much more superior than the other methods not only in terms of total deterioration, but also
in terms of total wins and losses.
%
\VSDMOEA{} was in the group of winning methods for 14 out of 19 functions, whereas the second best-ranked algorithm (\RMOEA{})
was in the group of winning methods for only 5 functions.
%
These conclusions are again quite similar to those drawn for the hypervolume in the main document.




\input{Tables/Table_IGDP_3obj.tex}
